---
title: "Fars functions"
author: "Kunasekaran Nirmalkanna"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package contains some function to extaract information from Fars data. Those functions are:


## 1. Read fars data using *fars_read()*.

This function reads a .csv file and convert in to \code{tbl} data frame object. The main advantage to using a tbl_df over a regular data frame is the printing: tbl objects only print a few rows and all the columns that fit on one screen, describing the rest of it as text.

* If there is no such file then it will return "file <filename> does not exist".

```{r}
library(Kanna)
fars_read("accident_2013.csv.bz2")
```


## 2. Generate fars data file name using *make_filename()*.

It generates character strings (eg: "accident_2013.csv.bz2") for
a given year (eg: 2013).

* If the argument is not a number then it will return "accident_NA.csv.bz2"
and a warning.

```{r}
make_filename(2013)
```



## 3. Extract month and year columns in the fars data using *fars_read_years()*.

This function returns a list of data frames. Each data frame contain only
the month and the year columns from fars data for each year. It returns a list of data frame for each year. The data frame contains only the month and the year columns of fars data.

* If the argument is not a number then it will return a NULL list with
a warning says that the argument is invalid.


```{r}
fars_read_years(2013)
fars_read_years(c(2013,2014))
```



## 4. Frequency table for months in fars data using *fars_summarize_years()*.

This function gives a frequency table for months in each year.

* It returns a frequency table for months in each year. The first column
of the output is the month number and the other columns are year-wise month
counts in the fars data.

* If the year is not in the fars data then it will return an error message.

```{r}
fars_summarize_years(2013)
fars_summarize_years(c(2013,2014))
```


## 5. Plot the accidents in states in the fars data using *fars_map_state()*.

This function plots the state and the point where the accidents
occured in a specific year.

* It returns a plot of state with points where the accidents
occured in a specific year.

* It plots the accidents which occured in latitude <= 90 and
longitude <= 900. If the argument \code{state.num} is beyond the number of
states in the fars data then it will return that "invalid STATE number".
If there is no accident during a specific year in  aspecific state then
it returns "no accidents to plot".

```{r echo=FALSE}
library(maps)
```

```{r fig.align='center'}
# fars_map_state(1,2013)
# fars_map_state(20,2015)
# fars_map_state(1,2014)
```
